---
title: "Study1_preliminary_analysis"
author: "Xiaotong Liu"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---


```{r warning=FALSE, include=FALSE, R preparatin include=FALSE}

# library(gridExtra)
# library(grid)
# library(ggplot2)
library(tidyverse)
library(jsonlite)
library(Hmisc)
library(stringdist)
library(stringr)

```


```{r message=FALSE, warning=FALSE, include=FALSE}
# load packages
# library(tidyverse)
# library(stringdist)
# library(stringr)
# 
# 
# 
# library(jsonlite)
# library(data.table)
# library(rtdists)
# library(cowplot)
# library(ggpubr)
# library(emmeans)
# library(lattice)
# library(afex)

# load function to create readme
```

## Prepare functions
```{r warning=FALSE, include=FALSE, prepare functions to encode event items include=FALSE}
encode_each_item <- function(x) {
  if (identical(x, "Eine zufällig ausgewählte Person in Deutschland spielt täglich Volleyball.")) {
    y <- "impl2_pos"
    
  } else if (identical(x, "Eine zufällig ausgewählte Person in Deutschland wird im Lauf ihres Lebens an Malaria erkranken.")){
    y <- "impl6_pos"
    
  } else if (identical(x, "Eine zufällig ausgewählte Person in Deutschland kann NICHT in mehr als vier Sprachen sprechen.")){
    y <- "impl4_neg"
    
  }  else if (identical(x, "Eine zufällig ausgewählte Person in Deutschland wurde NICHT in einem Krankenhaus geboren.")){
    y <- "plau6_neg"
    
    
  }  else if (identical(x, "Eine zufällig ausgewählte Person in Deutschland im Alter von 20 bis 25 Jahren studiert an einer Universität oder Hochschule.")){
    y <- "indiff2_pos"
    
  }  else if (identical(x, "Eine zufällig ausgewählte Person in Deutschland geht täglich mehr als 100 Schritte.")){
    y <- "plau4_pos"
    
  }  else if (identical(x, "In einem zufällig ausgewählten Krankenhaus in Deutschland wird das nächste Neugeborene KEIN Mädchen sein.")){
    y <- "check1_inbetween"
    
  }  else if (identical(x, "Eine zufällig ausgewählte deutsche Person ist Mitglied der christlichen Kirche.")){
    y <- "indiff12_pos"
    
  }  else if (identical(x, "Eine zufällig ausgewählte über 18-jährige Person in Deutschland hat KEINEN Bürojob.")){
    y <- "indiff6_neg"
    
  }  else if (identical(x, "An einem zufällig ausgewählten Tag im Jahr wird die Temperatur in Deutschland über 15 °C liegen.")){
    y <- "indiff11_pos"
    
  }  else if (identical(x, "Eine zufällig ausgewählte Person in Deutschland über 30 Jahre ist NICHT verheiratet.")){
    y <- "indiff1_neg"
    
  }  else if (identical(x, "In einem zufällig ausgewählten Jahr wird es in Deutschland im Juni NICHT schneien.")){
    y <- "impl3_neg"
    
  }  else if (identical(x, "Eine zufällig ausgewählte Person in Deutschland wohnt NICHT in Bayern, Baden-Württemberg oder Nordrhein-Westfalen.")){
    y <- "indiff3_neg"
    
    
  }  else if (identical(x, "Eine zufällig ausgewählte Person in Deutschland spielt NICHT täglich Volleyball.")){
    y <- "impl2_neg"
    
  } else if (identical(x, "In einem zufällig ausgewählten deutschen Haushalt findet man mindestens eine Waschmaschine.")){
    y <- "plau3_pos"
    
  } else if (identical(x, "Eine zufällig ausgewählte Person in Deutschland lebt NICHT im Saarland.")){
    y <- "impl5_neg"
    
  }  else if (identical(x, "Ein zufällig ausgewählter deutscher Erwachsener kann KEIN Fahrrad fahren.")){
    y <- "plau2_neg"
    
  }  else if (identical(x, "An einem zufällig ausgewählten Tag in Hamburg wird es Regen geben.")){
    y <- "indiff4_pos"
    
  }  else if (identical(x, "Eine zufällig ausgewählte Person in Deutschland besitzt KEIN Gerät, das sich mit dem Internet verbinden kann.")){
    y <- "plau5_neg"
    
  }  else if (identical(x, "An einem zufällig ausgewählten Tag im Jahr 2020 war Berlin die Hauptstadt Deutschlands.")){
    y <- "check_place1"
    
  }  else if (identical(x, "Eine zufällig ausgewählte Person in Deutschland ist Fan eines Fußballvereins.")){
    y <- "indiff9_pos"
    
  }  else if (identical(x, "Eine zufällig ausgewählte Person in Deutschland lebt NICHT in einer Großstadt.")){
    y <- "indiff7_neg"
    
  }  else if (identical(x, "Eine zufällig ausgewählte Person in Deutschland wird NICHT irgendwann an einer Herz-Kreislauf-Erkrankung sterben.")){
    y <- "indiff5_neg"
    
  }  else if (identical(x, "Eine zufällig ausgewählte Person in Deutschland über 30 Jahre ist verheiratet.")){
    y <- "indiff1_pos"
    
  }  else if (identical(x, "In einem zufällig ausgewählten Jahr wird es in Deutschland im Juni schneien.")){
    y <- "impl3_pos"
    
  }  else if (identical(x, "Eine zufällig ausgewählte Person in Deutschland wohnt in Bayern, Baden-Württemberg oder Nordrhein-Westfalen.")){
    y <- "indiff3_pos"
    
    
  } else if (str_detect(x, "ausgewählte Person in Deutschland hat NICHT mehr als")){
    y <- "impl1_neg"
    
  } else if (identical(x, "Eine zufällig ausgewählte Person in Deutschland wird im Lauf ihres Lebens NICHT an Malaria erkranken.")){
    y <- "impl6_neg"
    
  } else if (identical(x, "Eine zufällig ausgewählte Person in Deutschland lebt im Saarland.")){
    y <- "impl5_pos"
    
  }  else if (identical(x, "Ein zufällig ausgewählter deutscher Erwachsener kann Fahrrad fahren.")){
    y <- "plau2_pos"
    
  }  else if (identical(x, "Eine zufällig ausgewählte Person in Deutschland im Alter von 20 bis 25 Jahren studiert NICHT an einer Universität oder Hochschule.")){
    y <- "indiff2_neg"
    
  }  else if (identical(x, "Eine zufällig ausgewählte Person in Deutschland geht täglich NICHT mehr als 100 Schritte.")){
    y <- "plau4_neg"
    
  }  else if (identical(x, "An einem zufällig ausgewählten Tag im Jahr 2020 war Berlin NICHT die Hauptstadt Deutschlands.")){
    y <- "check_placelast"
    
  }  else if (identical(x, "Eine zufällig ausgewählte Person in Deutschland ist NICHT Fan eines Fußballvereins.")){
    y <- "indiff9_neg"
    
  }  else if (identical(x, "Eine zufällig ausgewählte Person in Deutschland lebt in einer Großstadt.")){
    y <- "indiff7_pos"
    
  }  else if (identical(x, "An einem zufällig ausgewählten Tag im Jahr wird die Temperatur in Deutschland NICHT über 15 °C liegen.")){
    y <- "indiff11_neg"
    
  }  else if (identical(x, "Ein zufällig ausgewählter Baum in Deutschland ist ein Laubbaum.")){
    y <- "indiff8_pos"
    
  }  else if (str_detect(x, "KEIN Englisch")){
    y <- "plau1_neg"
    
  }  else if (identical(x, "Ein zufällig ausgewähltes Auto auf der Straße in Deutschland wurde NICHT in Deutschland hergestellt.")){
    y <- "indiff10_neg"
    
    
  } else if (str_detect(x, "ausgewählte Person in Deutschland hat mehr als")){
    y <- "impl1_pos"
    
    
    
  } else if (identical(x, "In einem zufällig ausgewählten deutschen Haushalt findet man KEINE Waschmaschine.")){
    y <- "plau3_neg"
    
  } else if (identical(x, "Eine zufällig ausgewählte Person in Deutschland kann in mehr als vier Sprachen sprechen.")){
    y <- "impl4_pos"
    
  }  else if (identical(x, "Eine zufällig ausgewählte Person in Deutschland wurde in einem Krankenhaus geboren.")){
    y <- "plau6_pos"
    
  }  else if (identical(x, "An einem zufällig ausgewählten Tag in Hamburg wird es KEINEN Regen geben.")){
    y <- "indiff4_neg"
    
  }  else if (identical(x, "Eine zufällig ausgewählte Person in Deutschland besitzt mindestens ein Gerät, das sich mit dem Internet verbinden kann.")){
    y <- "plau5_pos"
    
  }  else if (identical(x, "In einem zufällig ausgewählten Krankenhaus in Deutschland wird das nächste Neugeborene ein Mädchen sein.")){
    y <- "check_inbetween2"
    
  }  else if (identical(x, "Eine zufällig ausgewählte deutsche Person ist NICHT Mitglied der christlichen Kirche.")){
    y <- "indiff12_neg"
    
  }  else if (identical(x, "Eine zufällig ausgewählte über 18-jährige Person in Deutschland hat einen Bürojob.")){
    y <- "indiff6_pos"
    
  }  else if (identical(x, "Eine zufällig ausgewählte Person in Deutschland wird irgendwann an einer Herz-Kreislauf-Erkrankung sterben.")){
    y <- "indiff5_pos"
    
  }  else if (identical(x, "Ein zufällig ausgewählter Baum in Deutschland ist KEIN Laubbaum.")){
    y <- "indiff8_neg"
    
  }  else if (str_detect(x, "spricht Englisch")){
    y <- "plau1_pos"
    
  }  else if (identical(x, "Ein zufällig ausgewähltes Auto auf der Straße in Deutschland wurde in Deutschland hergestellt.")){
    y <- "indiff10_pos"
    
    
  } else {
    y <- ""
    
  }  
  
  return(y)
}


encode_each_item_2 <- function(x) {
  
  events <- sapply(x,  function(x){x %>% str_split('\n')}) %>% unlist() %>% unique()
  
  
  eventsindex <- lapply(events, encode_each_item) %>% unlist() %>% as.character()
  
  return(eventsindex )
}
```


```{r warning=FALSE, include=FALSE, prepare functions to encode event items include=FALSE}
encode_each_item_three <- function(x) {
  if (identical(x, "impl_pos2")) {
    y <- "impl2_pos"
    
  } else if (identical(x, "impl_pos6")){
    y <- "impl6_pos"
    
  } else if (identical(x, "impl_neg4")){
    y <- "impl4_neg"
    
  }  else if (identical(x, "plau_neg6")){
    y <- "plau6_neg"
    
    
  }  else if (identical(x, "indiff_pos2")){
    y <- "indiff2_pos"
    
  }  else if (identical(x, "plau_pos4")){
    y <- "plau4_pos"
    
  }  else if (identical(x, "indiff_pos12")){
    y <- "indiff12_pos"
    
  }  else if (identical(x, "indiff_neg6")){
    y <- "indiff6_neg"
    
  }  else if (identical(x, "indiff_pos11")){
    y <- "indiff11_pos"
    
  }  else if (identical(x,  "indiff_neg1")){
    y <- "indiff1_neg"
    
  }  else if (identical(x, "impl_neg3")){
    y <- "impl3_neg"
    
  }  else if (identical(x, "indiff_neg3")){
    y <- "indiff3_neg"
    
  }  else if (identical(x, "impl_neg2")){
    y <- "impl2_neg"
    
  } else if (identical(x, "plau_pos3")){
    y <- "plau3_pos"
    
  } else if (identical(x, "impl_neg5")){
    y <- "impl5_neg"
    
  }  else if (identical(x, "plau_neg2")){
    y <- "plau2_neg"
    
  }  else if (identical(x, "indiff_pos4")){
    y <- "indiff4_pos"
    
  }  else if (identical(x, "plau_neg5")){
    y <- "plau5_neg"
    
  }  else if (identical(x, "indiff_pos9")){
    y <- "indiff9_pos"
    
  }  else if (identical(x, "indiff_neg7")){
    y <- "indiff7_neg"
    
  }  else if (identical(x, "indiff_neg5")){
    y <- "indiff5_neg"
    
  }  else if (identical(x, "indiff_pos1")){
    y <- "indiff1_pos"
    
  }  else if (identical(x, "impl_pos3")){
    y <- "impl3_pos"
    
  }  else if (identical(x, "indiff_pos3")){
    y <- "indiff3_pos"
    
  } else if (str_detect(x, "impl_neg1")){
    y <- "impl1_neg"
    
  } else if (identical(x, "impl_neg6")){
    y <- "impl6_neg"
    
  } else if (identical(x, "impl_pos5")){
    y <- "impl5_pos"
    
  }  else if (identical(x, "plau_pos2")){
    y <- "plau2_pos"
    
  }  else if (identical(x, "indiff_neg2")){
    y <- "indiff2_neg"
    
  }  else if (identical(x, "plau_neg4")){
    y <- "plau4_neg"
    
  }  else if (identical(x, "indiff_neg9")){
    y <- "indiff9_neg"
    
  }  else if (identical(x, "indiff_pos7")){
    y <- "indiff7_pos"
    
  }  else if (identical(x, "indiff_neg11")){
    y <- "indiff11_neg"
    
  }  else if (identical(x, "indiff_pos8")){
    y <- "indiff8_pos"
    
  }  else if (str_detect(x, "plau_neg1")){
    y <- "plau1_neg"
    
  }  else if (identical(x, "indiff_neg10")){
    y <- "indiff10_neg"
    
    
  } else if (str_detect(x, "impl_pos1")){
    y <- "impl1_pos"
    
    
    
  } else if (identical(x, "plau_neg3")){
    y <- "plau3_neg"
    
  } else if (identical(x, "impl_pos4")){
    y <- "impl4_pos"
    
  }  else if (identical(x, "plau_pos6")){
    y <- "plau6_pos"
    
  }  else if (identical(x, "indiff_neg4")){
    y <- "indiff4_neg"
    
  }  else if (identical(x, "plau_pos5")){
    y <- "plau5_pos"
    
  }  else if (identical(x, "indiff_neg12")){
    y <- "indiff12_neg"
    
  }  else if (identical(x, "indiff_pos6")){
    y <- "indiff6_pos"
    
  }  else if (identical(x, "indiff_pos5")){
    y <- "indiff5_pos"
    
  }  else if (identical(x, "indiff_neg8")){
    y <- "indiff8_neg"
    
  }  else if (str_detect(x, "plau_pos1")){
    y <- "plau1_pos"
    
  }  else if (identical(x, "indiff_pos10")){
    y <- "indiff10_pos"
    
    
  } else {
    y <- ""
    
  }  
  
  return(y)
}


```






## Prepare data sets 

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Read in data 

data0 <- read_file('person_186.txt') %>% # Read the text file from JATOS ...
          str_split('\n') %>% first() %>%   # ... split it into lines ...
          discard(function(x) x == '') %>%   # ... filter empty rows ...
          map_dfr(fromJSON, flatten=T)


data <- data0 %>% 
          filter(sender %in% c("Welcome","Consent",  # keep only rows with useful information -> filter by sender 
                               "study screen", "Demographic control","Post-study questionnaire"))   %>% 
          select(ID = url.srid, # select ( & rename) only variables of interest
                 sender, 
                 condition,
                 f00,
                 duration:time_switch,eveTopleft:eveDownright_type, rank_Order_one: rank_Order_four) %>%
  mutate(eveTopleft = eveTopleft_type,
         eveTopright = eveTopright_type,
         eveDownleft = eveDownleft_type,
         eveDownright = eveDownright_type) %>%
  fill(ID,.direction = "down") %>%
  group_by(ID) %>%
  fill(condition, .direction = "updown") %>%
  select(-eveTopleft_type, -eveTopright_type, -eveDownleft_type, -eveDownright_type)



#remove NAs
data_clean <- data

data_clean$rank_1<- sapply(data_clean$rank_Order_one,  encode_each_item_2) 
data_clean$rank_2 <- sapply(data_clean$rank_Order_two,  encode_each_item_2)
data_clean$rank_3 <- sapply(data_clean$rank_Order_three,  encode_each_item_2)
data_clean$rank_4 <- sapply(data_clean$rank_Order_four,  encode_each_item_2)

data_clean$rank_1[sapply(data_clean$rank_1, function(x){identical(x, character(0))})] <- "_"
data_clean$rank_2[sapply(data_clean$rank_2, function(x){identical(x, character(0))})] <- "_"
data_clean$rank_3[sapply(data_clean$rank_3, function(x){identical(x, character(0))})] <- "_"
data_clean$rank_4[sapply(data_clean$rank_4, function(x){identical(x, character(0))})] <- "_"
```

Participants exclusions:

Exclusion criterion (1): According to if participants passed the understanding (or in other words attention) check items by giving "correct" rankings ... AS a results, we excluded 7 participants in condition A where participants are allowed to give ties and 1 participant in condition B where participants are not allowed to give ties.

Exclusion criterion (2): One participant stated that he/she did not speak German. I excluded this one, even though he made comments in the end and indicated he/she was serious - Not sure about this

```{r echo=FALSE, message=FALSE, warning=FALSE}
#### check attention check items 
#### one participant stated that he/she did not speak German. I decided to exclude this one, even though he made comments in the end and indicated he/she was serious. his/her id: 2969, belongs to condition A
data2 <- data_clean %>% filter(f00 == "7") %>%
  filter((rank_4 != "check_placelast" & rank_3 != "check_placelast") | (rank_1 != "check_place1") )


### 
data2 %>% group_by(condition) %>% count() 

#### So, we end up excluding (8+1) 9 participants. 8 did not pass attention check items and 1 stated that he/she did not speak 

data_clean <- data_clean %>%
  filter(ID %nin% c(data2$ID, 2969)) %>% 
  filter(f00 != 7)


data_clean <- data_clean %>%  
  select(ID, condition, f00, duration, eveTopleft: eveDownright, rank_1: rank_4) %>%
  drop_na()



# data_clean %>% group_by(ID) %>% count()
```

Let's have a look at the demographic information about our participants.


### Prepare data set one with demographic information only

```{r echo=FALSE, message=FALSE, warning=FALSE}
data_demo <- data0 %>% 
          filter(sender %in% c("Welcome","Consent",  # keep only rows with useful information -> filter by sender 
                               "Demographic control","Post-study questionnaire"))   %>% 
          select(ID = url.srid, # select ( & rename) only variables of interest
                 sender, 
                 condition,
                 age:comments) %>%
  fill(ID,.direction = "down") %>%
  group_by(ID) %>%
  fill(condition, .direction = "updown") %>%
  fill(quality, .direction = "updown") %>%
  fill(comments, .direction = "updown") %>%
  drop_na()

data_demo2 <- data_demo %>%
  filter(ID %in% unique(data_clean$ID))

head(data_demo2)
```

See below, the comments that participants gave:
```{r echo=FALSE, message=FALSE, warning=FALSE}

unique(data_demo2$comments)
```

See below, MEAN and SD age of the participants
```{r echo=FALSE, message=FALSE, warning=FALSE, prepare demographic data set include=FALSE}
data_demo2$age <- data_demo2$age  %>%  str_remove_all("\\D+")

mean(data_demo2$age %>% as.numeric())
sd(data_demo2$age %>% as.numeric())

#ggplot(data_demo, aes(x=age)) + geom_bar()
```

See below the gender distribution of participants. 
```{r echo=FALSE, message=FALSE, warning=FALSE, prepare demographic data set include=FALSE}
data_demo2 %>% group_by(gender) %>% count()
```

What are the comments given by all participants without any exclusions?
```{r echo=FALSE, message=FALSE, warning=FALSE, prepare demographic data set include=FALSE}
######### before excluding any participants, how's the demographic information like ?
data_demo <- data0 %>% 
          filter(sender %in% c("Welcome","Consent",  # keep only rows with useful information -> filter by sender 
                               "Demographic control","Post-study questionnaire"))   %>% 
          select(ID = url.srid, # select ( & rename) only variables of interest
                 sender, 
                 condition,
                 age:comments) %>%
  fill(ID,.direction = "down") %>%
  group_by(ID) %>%
  fill(condition, .direction = "updown") %>%
  fill(quality, .direction = "updown") %>%
  fill(comments, .direction = "updown") %>%
  drop_na()

data_demo$age <- data_demo$age  %>%  str_remove_all("\\D+")


#### age, gender distribution, subject & employment distribution 
unique(data_demo$comments)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, prepare demographic data set include=FALSE}

# mean(data_demo$age %>% as.numeric())
# sd(data_demo$age %>% as.numeric())

#ggplot(data_demo, aes(x=age)) + geom_bar()
```

```{r echo=FALSE, message=FALSE, warning=FALSE, prepare demographic data set include=FALSE}
# data_demo %>% group_by(gender) %>% count()
```

### Prepare data set two with responses and response time only

We need to add three columns (i.e.,three DVs).The first DV is whether there is a logical error in the provided ranking. The second is what type of error it has if the provided ranking has a logical error. The third is whether the provided ranking includes ties or not. For data set B, this DV should always be equal to 0.


Add the first DV - if there is a logical error or not in the provided ranking.




```{r Prepare functions to judge if logical or not include=FALSE}
######### Next the most important step: check if each response is logical or not 

######### use pmap() function 

judge_rank <- function(rank_1,rank_2,rank_3,rank_4) {
  
  
  if(rank_1 != "_" && rank_2 != "_" && rank_3 != "_" && rank_4 != "_"){
    if_ties <- "no"
  } else {
    if_ties <- "yes"
  }
  
  if ( if_ties == "yes" && rank_1 != "_" && rank_2 != "_" && rank_3 != "_" && rank_4 == "_" ){
   if_ties = "three"
  } else if ( if_ties == "yes" && rank_1 != "_" && rank_2 != "_" && rank_3 == "_" && rank_4 == "_" ){
    if_ties = "two"
  } else if ( if_ties == "yes" && rank_1 != "_" && rank_2 == "_" && rank_3 == "_" && rank_4 == "_" ) {
    if_ties = "one"
  } else {
    if_ties = if_ties
  }
  
  
  if ( if_ties == "three" && is.na( stringdist(rank_2[1], rank_2[2])) == FALSE ) {
    place_with_ties <- 2 
  } else if ( if_ties == "three" && is.na( stringdist(rank_1[1], rank_1[2])) == FALSE){
    place_with_ties <- 1
  } else if ( if_ties == "three" && is.na( stringdist(rank_3[1], rank_3[2])) == FALSE){
    place_with_ties <- 3
  } else {
    place_with_ties <- 0
  }
 
   
  if ( if_ties == "two" && length(rank_1) == 2 && length(rank_2) == 2){
    two_fields <- "even"
  } else if( if_ties == "two" && ( length(rank_1) != 2 | length(rank_2) != 2) ){
    two_fields <- "uneven"
  } else{
    two_fields <- "not_relevant"
  }

  
  if(if_ties == "no" && stringdist(rank_1, rank_4) == 3 && stringdist(rank_2, rank_3) == 3 ){
    return(0)
  } else if (if_ties == "no" && (stringdist(rank_1, rank_4) != 3 | stringdist(rank_2, rank_3) != 3 ) ){
    return(1)
  } else if( if_ties == "three" && place_with_ties == 2 && stringdist(rank_1, rank_3) == 3 && stringdist(rank_2[1], rank_2[2]) == 3){
    return(0)
  } else if( if_ties == "three" && place_with_ties == 2 && stringdist(rank_1, rank_3) != 3 && stringdist(rank_2[1], rank_2[2]) != 3 ){
    return(1)
  } else if( if_ties == "three" && place_with_ties == 3 ){
    return(1)
  } else if( if_ties == "three" && place_with_ties == 1){
    return(1)
  } else if ( if_ties == "two" && two_fields == "even" && stringdist(rank_1[1], rank_1[2]) != 3 && stringdist(rank_2[1], rank_2[2]) != 3 ){
    return(0)
  } else if (if_ties == "two" && two_fields == "even" && stringdist(rank_1[1], rank_1[2]) == 3 && stringdist(rank_2[1], rank_2[2]) == 3) {
    return(1)
  } else if (if_ties == "two" && two_fields == "uneven") {
    return(1)
  } else if (if_ties == "one") {
    return(0)
  } else {
    return(-1)
  }

}


input_list <- data_clean %>% select(ID, rank_1, rank_2, rank_3, rank_4)
input_list$ID <- NULL

data_clean$logical_pass <- pmap_dbl(input_list, judge_rank)


data_clean$con <- ifelse(str_detect(data_clean$eveTopleft, "diff"), "indiff", "extreme")

#data_clean %>% group_by(con) %>% count() ###validation check, pass
```


Before we go on, we re-index events under presentation orders
```{r}

############ start from eveTopleft
judge_eveTopleft <- function(eveTopleft){
  if ( grepl("_pos", eveTopleft, fixed=TRUE) ) {
    eve = "A"
  } else if ( grepl("_neg", eveTopleft, fixed=TRUE) ) {
       eve = "a"
  }
  
  return(eve)
}

data_clean <- data_clean %>% 
  mutate(place_1 = sapply(eveTopleft, judge_eveTopleft))


########### then judge eveTopright

judge_eveTopright <- function(eveTopleft, eveTopright){
  
  if( stringdist(eveTopleft, eveTopright) == 3 && grepl("_pos", eveTopright, fixed=TRUE) ){
    eve = "A"
  } else if ( stringdist(eveTopleft, eveTopright) == 3 && grepl("_neg", eveTopright, fixed=TRUE) ) {
    eve = "a"
  } else if ( stringdist(eveTopleft, eveTopright) != 3 && grepl("_pos", eveTopright, fixed=TRUE) ){
    eve = "B"
  } else if ( stringdist(eveTopleft, eveTopright) != 3 && grepl("_neg", eveTopright, fixed=TRUE)  ){
    eve = "b"
  }
  
}

input_list <- data_clean %>% select(ID, eveTopleft, eveTopright)
input_list$ID <- NULL

data_clean$place_2 <- pmap_chr(input_list, judge_eveTopright)

############ then eveDownleft

judge_eveDownleft <- function(eveTopleft, eveDownleft){
  
  if( stringdist(eveTopleft, eveDownleft) == 3 && grepl("_pos", eveDownleft, fixed=TRUE) ){
    eve = "A"
  } else if ( stringdist(eveTopleft, eveDownleft) == 3 && grepl("_neg", eveDownleft, fixed=TRUE) ) {
    eve = "a"
  } else if ( stringdist(eveTopleft, eveDownleft) != 3 && grepl("_pos", eveDownleft, fixed=TRUE) ){
    eve = "B"
  } else if ( stringdist(eveTopleft, eveDownleft) != 3 && grepl("_neg", eveDownleft, fixed=TRUE)  ){
    eve = "b"
  }
  
}

input_list <- data_clean %>% select(ID, eveTopleft, eveDownleft)
input_list$ID <- NULL

data_clean$place_3 <- pmap_chr(input_list, judge_eveDownleft)

############ then eveDownright

judge_eveDownright <- function(eveTopleft, eveDownright){
  
  if( stringdist(eveTopleft, eveDownright) == 3 && grepl("_pos", eveDownright, fixed=TRUE) ){
    eve = "A"
  } else if ( stringdist(eveTopleft, eveDownright) == 3 && grepl("_neg", eveDownright, fixed=TRUE) ) {
    eve = "a"
  } else if ( stringdist(eveTopleft, eveDownright) != 3 && grepl("_pos", eveDownright, fixed=TRUE) ){
    eve = "B"
  } else if ( stringdist(eveTopleft, eveDownright) != 3 && grepl("_neg", eveDownright, fixed=TRUE)  ){
    eve = "b"
  }
  
}

input_list <- data_clean %>% select(ID, eveTopleft, eveDownright)
input_list$ID <- NULL

data_clean$place_4 <- pmap_chr(input_list, judge_eveDownright)



#view(data_clean)

data_clean <- data_clean %>% 
  mutate(presentation_order = paste0(place_1, "_", place_2, "_", place_3, "_", place_4))

data_clean <- data_clean %>%
  mutate(eveTopleft = sapply(eveTopleft, encode_each_item_three),
         eveTopright = sapply(eveTopright, encode_each_item_three),
         eveDownleft = sapply(eveDownleft, encode_each_item_three),
         eveDownright = sapply(eveDownright, encode_each_item_three)) %>% select(-place_1, -place_2, -place_3, -place_4)

```



Before we add the other two DVs, we need to divide the dataset first. Let's divide the dataset into dataset A where participants are allowed to give ties and dataset B where participants are not allowed to give ties.

##### Let's start with dataset_B.

```{r separate data set into dataset A and dataset B include=FALSE}
data_clean_A <- data_clean %>% filter(condition == "A")
data_clean_B <- data_clean %>% filter(condition == "B")
```

Add the second DV to dataset_B
```{r separate data set into dataset A and dataset B include=FALSE}

judge_B_error_type <- function(rank_1, rank_2, rank_3, rank_4, logical_pass) {
  
  if (logical_pass == 0) {
    error_type = NA
  } else {
    
    if(stringdist(rank_1, rank_2) == 3 & stringdist(rank_3, rank_4) == 3){
      error_type = 1
    } else {
    error_type = 0
    }
    
  }
  
  return(error_type)
}

input_list <- data_clean_B %>% select(ID, rank_1, rank_2, rank_3, rank_4, logical_pass) 
input_list$ID <- NULL


data_clean_B$error_type <- pmap_chr(input_list, judge_B_error_type)

```

Add the third DV to dataset_B
```{r message=FALSE, warning=FALSE, include=FALSE}
data_clean_B$if_ties <- NA
```





That's it for dataset_B.


#### Let's continue to deal with dataset_A.

We've already add the first DV, namely if the ranking has a logical error or not. Now, let's add the second DV, namely what type of error the ranking has.

##### For data_set A, there are three types of logically incorrect rankings.
```{r}

## I need to further divide the data set _A based on the number of ties used in the rankings and the position of the ties in the rankings.

judge_if_ties <- function(rank_1, rank_2, rank_3, rank_4) {
  
  if (rank_1 != "_" && rank_2 != "_" && rank_3 != "_" && rank_4 != "_") {
    if_ties = 4
  } else if ( rank_1 != "_" && rank_2 != "_" && rank_3 != "_" && rank_4 == "_" ){
   if_ties = 3
  } else if ( rank_1 != "_" && rank_2 != "_" && rank_3 == "_" && rank_4 == "_" ){
    if_ties = 2
  } else if ( rank_1 != "_" && rank_2 == "_" && rank_3 == "_" && rank_4 == "_" ) {
    if_ties = 1
  } else {
    if_ties = "error"
  }
  
  return(if_ties)
}

input_list <- data_clean_A %>% select(ID, rank_1, rank_2, rank_3, rank_4) 
input_list$ID <- NULL

data_clean_A$if_ties <- pmap_dbl(input_list, judge_if_ties) 


########################## use four fields ##########################
data_clean_A_four <- data_clean_A %>% filter(if_ties == 4) 


input_list <- data_clean_A_four %>% select(ID, rank_1, rank_2, rank_3, rank_4, logical_pass) 
input_list$ID <- NULL


data_clean_A_four$error_type <- pmap_chr(input_list, judge_B_error_type)


########################## use three fields ##########################


data_clean_A_three <- data_clean_A %>% filter(if_ties == 3) 


judge_A_three_where <- function(rank_1, rank_2, rank_3, rank_4) {
  
  if ( is.na( stringdist(rank_2[1], rank_2[2])) == FALSE ) {
    place_with_ties = 2 
  } else if ( is.na( stringdist(rank_1[1], rank_1[2])) == FALSE){
    place_with_ties = 1
  } else if ( is.na( stringdist(rank_3[1], rank_3[2])) == FALSE){
    place_with_ties = 3
  } else {
    place_with_ties = 0
  }
  return(place_with_ties)
}

input_list <- data_clean_A_three %>% select(ID, rank_1, rank_2, rank_3, rank_4) 
input_list$ID <- NULL


data_clean_A_three$ties_where <- pmap_dbl(input_list, judge_A_three_where) 

############## ties in the first field #############

data_clean_A_three_where_one <- data_clean_A_three %>%
  filter(ties_where == 1)


judge_error_A_three_where_one <- function(rank_1, logical_pass) {
  
  type <- NA
  
  if (logical_pass == 1 && stringdist(rank_1[1], rank_1[2]) == 3) {
    type = 1
  } else if ( logical_pass == 1 && stringdist(rank_1[1], rank_1[2]) != 3 ){
    type = 0
  }
  return(type)
}


input_list <- data_clean_A_three_where_one %>% select(ID, rank_1, logical_pass) 
input_list$ID <- NULL


data_clean_A_three_where_one$error_type <- pmap_chr(input_list, judge_error_A_three_where_one) 





############## ties in the second field #############
data_clean_A_three_where_two <- data_clean_A_three %>%
  filter(ties_where == 2) 

judge_error_A_three_where_two <- function(rank_2, logical_pass){
  
  type <- NA
    
  if(logical_pass == 1 && stringdist(rank_2[1], rank_2[2]) != 3){
    type = 2
  } 
  return(type)
  
}

input_list <- data_clean_A_three_where_two %>% select(ID, rank_2, logical_pass) 
input_list$ID <- NULL


data_clean_A_three_where_two$error_type <- pmap_chr(input_list, judge_error_A_three_where_two) 

############## ties in the third field #############
data_clean_A_three_where_three <- data_clean_A_three %>%
  filter(ties_where == 3) 


judge_error_A_three_where_three <- function(rank_3, logical_pass) {
  
  type <- NA
  
  if (logical_pass == 1 && stringdist(rank_3[1], rank_3[2]) == 3 ) {
    type = 1
  } else if (logical_pass == 1 && stringdist(rank_3[1], rank_3[2]) != 3) {
    type = 0
  }
  
  return(type)
  
}

input_list <- data_clean_A_three_where_three %>% select(ID, rank_3, logical_pass)

input_list$ID <- NULL

data_clean_A_three_where_three$error_type <- pmap_chr(input_list, judge_error_A_three_where_three)


############

data_clean_A_three <- rbind(data_clean_A_three_where_one, data_clean_A_three_where_two, data_clean_A_three_where_three) %>% select(-ties_where)


########################## use two fields ##########################
data_clean_A_two <- data_clean_A %>% filter(if_ties == 2) 

judge_error_A_two <- function(rank_1, rank_2, logical_pass) {
  
  type <- NA
    
  if (logical_pass == 1 && length(rank_1) == 2 && length(rank_2) == 2) {
    type = 1
  } else if (logical_pass == 1 && length(rank_1) != 2 &&  length(rank_2) != 2 ){
    type = 2
  } else if (logical_pass == 0) {
    type = NA
  }
  
  return(type)
}

input_list <- data_clean_A_two %>% select(ID, rank_1, rank_2, logical_pass)
input_list$ID <- NULL

data_clean_A_two$error_type <- pmap_chr(input_list, judge_error_A_two)

########################## use one field ##########################
data_clean_A_one <- data_clean_A %>% filter(if_ties == 1) 

data_clean_A_one$error_type <- NA


data_clean_A <- rbind(data_clean_A_four, data_clean_A_three, data_clean_A_two, data_clean_A_one) 


```















#### Now let add the last (DV), if the ranking include ties or not.

```{r echo=FALSE, message=FALSE, warning=FALSE}
judge_if_ties <- function(rank_1, rank_2, rank_3, rank_4) {
  
  if (rank_1 != "_" && rank_2 != "_" && rank_3 != "_" && rank_4 != "_") {
    if_ties = 0
  } else {
   if_ties = 1
  } 
  
  return(if_ties)
}

input_list <- data_clean_A %>% select(ID, rank_1, rank_2, rank_3, rank_4) 
input_list$ID <- NULL

data_clean_A$if_ties <- pmap_dbl(input_list, judge_if_ties) 

```


Now, let's combine dataset A with dataset B.

```{r}
df <- rbind(data_clean_A, data_clean_B)
```


######## Now I need to re-write, rank_1, rank_2, rank_3, rank_4, then I can save the clean data set. 
```{r}
clean_rank <- function (rank) {
  if (length(rank) == 1) {
    cleaned_str = toString(rank[1])
  } else if (length(rank) == 2) {
    cleaned_str = paste(rank[1], "&", rank[2])
  }  else if (length(rank) == 3) {
    cleaned_str = paste(rank[1], "&", rank[2], "&", rank[3])
  }  else if (length(rank) == 4) {
    cleaned_str = paste(rank[1], "&", rank[2], "&", rank[3], "&", rank[4])
  }
} 

df <- df %>% 
  mutate(rank_1 = sapply(rank_1, clean_rank),
         rank_2 = sapply(rank_2, clean_rank),
         rank_3 = sapply(rank_3, clean_rank),
         rank_4 = sapply(rank_4, clean_rank)) 


df <- df %>% select(ID, condition, con, f00, duration, presentation_order, eveTopleft:eveDownright, 
                    rank_1:rank_4, logical_pass, error_type, if_ties)

#view(df)


df <- df %>%
  mutate(condition = gsub("A", "ties_allowed", condition)) 
  
  
df <-  df %>%
  mutate(condition = gsub("B", "ties_not_allowed", condition))

df <- df %>%
  mutate(error_type = as.numeric(error_type))


df <- df %>%
  mutate(classify_all_ranks = ifelse(is.na(error_type), "logical", 
                                    ifelse(error_type == 1, "type_1",
                                           ifelse(error_type == 0, "type_2",
                                                  ifelse(error_type == 2, "type_3", "error")))))

view(df)
```





```{r}
colnames(df)[2] <- "between_subject_condition"
colnames(df)[3] <- "within_subject_condition"
colnames(df)[15] <- "if_there_are_errors"
colnames(df)[16] <- "error_type"
colnames(df)[17] <- "if_there_are_ties"



```



```{r}
write.csv(df, "study_1_df.csv", row.names=FALSE)
write.csv(data_demo2, "df_data_demo2.csv", row.names=FALSE)
write.csv(data_demo, "df_data_demo.csv", row.names=FALSE)
```




