---
title: "Progress tracing: Testing sampling based models of probability estimations"
shorttitle: "Progress tracing"
author: "Xiaotong Liu"
date: "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\. %B %Y')`"
output:
  pdf_document:
    toc: true
    toc_depth: 4
---

```{r}

library(tidyverse)
library(afex)
library(emmeans)
library(runjags)
library(TreeBUGS)
library(tidybayes)
library(ggpubr)
library(latex2exp)

```



# 1. Simulation 
## 1.1 Code

For the complete code, please see the file "".

## 1.2 Results

# 2. Experiment 1

## 2.1 Demographic information
## 2.2 Descriptive statistics 
## 2.3 MPT analysis
### 2.3.1 Prepare data sets.

We prepared two date sets, one for the group of participants that were allowed to give ties in the rankings, and one for the group of participants that were not allowed to give ties in the rankings.

To use MPT models to analyse data, we need to prepare data with individual frequencies. In the data table, each row is one person and each column is one category. Each cell is the frequency of giving one category of responses by one person.


```{r}

 df <- read.csv("study_1_df.csv")
 # 
 # indiff_allow_indi <- df %>%
 #   filter(between_subject_condition == "ties_allowed",
 #          within_subject_condition == "indiff") %>%
 #   pivot_wider(names_from = classify_all_ranks, values_from = f00) %>%
 #   group_by(ID) %>%
 #   select(ID, between_subject_condition, within_subject_condition,
 #          logical, type_1, type_2, type_3) %>%
 #   mutate(logical = ifelse(is.na(logical) == TRUE, 0, 1),
 #          type_1 = ifelse(is.na(type_1) == TRUE, 0, 1),
 #          type_2 = ifelse(is.na(type_2) == TRUE, 0, 1),
 #          type_3 = ifelse(is.na(type_3) == TRUE, 0, 1)) %>%
 #   group_by(ID) %>%
 #   summarise(condition = "ties_allowed",
 #             ML = sum(logical),
 #             M1 = sum(type_1),
 #             M2 = sum(type_2),
 #             M3 = sum(type_3))

 # edge_allow_indi <- df %>%
 #   filter(between_subject_condition == "ties_allowed",
 #          within_subject_condition == "extreme") %>%
 #   pivot_wider(names_from = classify_all_ranks, values_from = f00) %>%
 #   group_by(ID) %>%
 #   select(ID, between_subject_condition,  within_subject_condition,
 #          logical, type_1, type_2, type_3) %>%
 #   mutate(logical = ifelse(is.na(logical) == TRUE, 0, 1),
 #          type_1 = ifelse(is.na(type_1) == TRUE, 0, 1),
 #          type_2 = ifelse(is.na(type_2) == TRUE, 0, 1),
 #          type_3 = ifelse(is.na(type_3) == TRUE, 0, 1)) %>%
 #   group_by(ID) %>%
 #   summarise(EL = sum(logical),
 #             E1 = sum(type_1),
 #             E2 = sum(type_2),
 #             E3 = sum(type_3))
 # 
 # allow_indi <- cbind(indiff_allow_indi, edge_allow_indi %>% select(-ID))



 # indiff_not_allow_indi <- df %>% filter(between_subject_condition == "ties_not_allowed", within_subject_condition == "indiff") %>%
 #   pivot_wider(names_from = classify_all_ranks, values_from = f00) %>%
 #   group_by(ID) %>%
 #   select(ID, between_subject_condition,  within_subject_condition,
 #          logical, type_1, type_2) %>%
 #   mutate(logical = ifelse(is.na(logical) == TRUE, 0, 1),
 #          type_1 = ifelse(is.na(type_1) == TRUE, 0, 1),
 #         type_2 = ifelse(is.na(type_2) == TRUE, 0, 1)) %>%
 #   group_by(ID) %>%
 #   summarise(condition = "ties_not_allowed",
 #             ML = sum(logical),
 #             M1 = sum(type_1),
 #             M2 = sum(type_2)) %>% unique()
 # 
 # edge_not_allow_indi <- df %>%
 #   filter(between_subject_condition == "ties_not_allowed",
 #          within_subject_condition == "extreme") %>%
 #   pivot_wider(names_from = classify_all_ranks, values_from = f00) %>%
 #   group_by(ID) %>%
 #   select(ID, between_subject_condition,  within_subject_condition,
 #          logical, type_1, type_2) %>%
 #   mutate(logical = ifelse(is.na(logical) == TRUE, 0, 1),
 #          type_1 = ifelse(is.na(type_1) == TRUE, 0, 1),
 #          type_2 = ifelse(is.na(type_2) == TRUE, 0, 1)) %>%
 #   group_by(ID) %>%
 #   summarise(EL = sum(logical),
 #             E1 = sum(type_1),
 #             E2 = sum(type_2)) %>% unique()
 # 
 # not_allow_indi <- cbind(indiff_not_allow_indi, edge_not_allow_indi %>% select(-ID))
 # 
 # write.csv(allow_indi, "allow_indi.csv", row.names = FALSE)
 # write.csv(not_allow_indi, "not_allow_indi.csv", row.names = FALSE)
 # 
 # head(allow_indi)
 # head(not_allow_indi)


```

### 2.3.2 when ties are allowed

```{r}
# allow_traitMPT <- traitMPT(eqnfile="allow_rank.eqn",
#          data="allow_indi.csv",
#          transformedParameters =list("deltal=lm-le", "deltat3 =t3m-t3e", "deltat1 = t1m-t1e"),
#          parEstFile = "results_allow_traitMPT.txt",
#          n.iter = 200000,             # number of iterations
#          n.burnin = 50000,            # number of burnin samples that are removed
#          n.thin = 100,                 # thinning rate of removing samples
#          n.chains = 4)
# 
# save(allow_traitMPT, file = "allow_traitMPT.rda")

# not_allow_traitMPT <- traitMPT(eqnfile="not_allow_rank.eqn",
#                                data = "not_allow_indi.csv",
#                                transformedParameters =list("deltal=lm-le", "deltat1 = t1m-t1e"),
#                                parEstFile = "results_not_allow_traitMPT.txt",
#                                n.iter = 200000,
#                                n.burnin = 50000,
#                                n.thin = 100, 
#                                n.chains = 4)
# 
# save(not_allow_traitMPT, file = "not_allow_traitMPT.rda")
```


```{r}

## prepare the figure 
load("allow_traitMPT.rda")
load("not_allow_traitMPT.rda")


sample_allow_traitMPT <- getSamples(allow_traitMPT, "mean")
sample_not_allow_traitMPT <- getSamples(not_allow_traitMPT, "mean")

############# run the test 
tidy_sample_allow_traitMPT <- tidy_draws(sample_allow_traitMPT) %>%
  mutate(delta_l = `mean[1]_le` - `mean[2]_lm`,
         delta_t1 = `mean[4]_t1m` - `mean[3]_t1e`,
         delta_t3 = `mean[6]_t3m` - `mean[5]_t3e`,
         bw = "Ties allowed",
         delta_l_test_prep = ifelse(delta_l > 0, 1, 0),
         delta_t1_test_prep = ifelse(delta_t1 > 0, 1, 0),
         delta_t3_test_prep = ifelse(delta_t3 > 0, 1, 0))

tidy_sample_not_allow_traitMPT  <- tidy_draws(sample_not_allow_traitMPT) %>%
  mutate(delta_l = `mean[1]_le` - `mean[2]_lm`,
         delta_t1 = `mean[4]_t1m` - `mean[3]_t1e`,
         bw = "Ties not allowed",
         delta_l_test_prep = ifelse(delta_l > 0, 1, 0),
         delta_t1_test_prep = ifelse(delta_t1 > 0, 1, 0)) 

allow_delta_l_test <- sum(tidy_sample_allow_traitMPT$delta_l_test_prep) / nrow(tidy_sample_allow_traitMPT)
allow_delta_t1_test <- sum(tidy_sample_allow_traitMPT$delta_t1_test_prep) / nrow(tidy_sample_allow_traitMPT)
allow_delta_t3_test <- sum(tidy_sample_allow_traitMPT$delta_t3_test_prep) / nrow(tidy_sample_allow_traitMPT)


not_allow_delta_l_test <- sum(tidy_sample_not_allow_traitMPT$delta_l_test_prep) / nrow(tidy_sample_not_allow_traitMPT)
not_allow_delta_t1_test <- sum(tidy_sample_not_allow_traitMPT$delta_t1_test_prep) / nrow(tidy_sample_not_allow_traitMPT)


############# plot the figure (difference distribution)

 
tidy_sample_two_btws_condition <- rbind(tidy_sample_allow_traitMPT %>%
  pivot_longer(c(delta_l, delta_t1, delta_t3), 
               names_to = "parameter_name",
               values_to = "parameter_value") %>% 
   select(parameter_name, parameter_value, bw), tidy_sample_not_allow_traitMPT %>%
  pivot_longer(c(delta_l, delta_t1), 
               names_to = "parameter_name",
               values_to = "parameter_value") %>% 
   select(parameter_name, parameter_value, bw)) %>%
  mutate(parameter_name = as.factor(parameter_name))


tidy_sample_two_btws_condition$parameter_name <- factor(tidy_sample_two_btws_condition$parameter_name,
                                                        labels=c('delta_l'= "l", 'delta_t1' = "t1", 'delta_t2'= "t2"))


tidy_sample_two_btws_condition %>%
    ggplot(aes(x = parameter_value)) +
  stat_halfeye() + theme_set(theme_bw()) +
   geom_vline(xintercept=0, linetype="dashed", color = "black", size=1) +
  facet_wrap(bw~parameter_name) + 
    xlab("Difference in group-level parameter estimates") + 
  ylab("Density")
   


ggsave("p_study1.pdf")


 # p1 <- tidy_sample_allow_traitMPT %>% 
 #    mutate(delta_l = `mean[1]_le` - `mean[2]_lm`) %>% 
  # ggplot(aes(x = delta_l)) +
  # stat_halfeye() + theme_set(theme_bw()) + xlab("l")  + ylab("density") +
  #  geom_vline(xintercept=0, linetype="dashed", color = "black", size=1) +
  #  theme(axis.title.y = element_blank(),
  #       axis.text.y =element_blank(),
  #       axis.ticks.y = element_blank())


# p2 <- tidy_sample_allow_traitMPT %>% 
#     mutate(delta_t1 = `mean[4]_t1m` - `mean[3]_t1e` ) %>% 
#   ggplot(aes(x = delta_t1)) +
#   stat_halfeye() + theme_set(theme_bw()) + xlab("t1")  + 
#    geom_vline(xintercept=0, linetype="dashed", color = "black", size=1) + 
#    theme(axis.title.y = element_blank(),
#         axis.text.y =element_blank(),
#         axis.ticks.y = element_blank())



# p3 <- tidy_sample_allow_traitMPT %>% 
#     mutate(delta_t3 = `mean[6]_t3m` - `mean[5]_t3e`) %>% 
#   ggplot(aes(x = delta_t3)) +
#   stat_halfeye() + theme_set(theme_bw()) + xlab("t3")  + 
#    geom_vline(xintercept=0, linetype="dashed", color = "black", size=1)  + 
#    theme(axis.title.y = element_blank(),
#         axis.text.y =element_blank(),
#         axis.ticks.y = element_blank())

# ggarrange(p1, p2, p3, ncol = 3, nrow = 1)
    
    
    
```




